\noindent
\textbf{\LARGE Definitions and Theorems} \\
\large Week: Oct. 28 - Nov. 1

\normalsize


\section*{Theorems, Propositions, Corollaries}
\subsection*{2.3 Kernel and Image of a Linear Map}

\textbf{Thm 2.3.17 [Rank-Nullity Thm]:} Let $V$ be an n-dimensional vector space and $T: V \rightarrow W$ be a linear map. Then dim(ker($T$)) + dim(im($T$)) = dim($V$).

\subsection*{2.4 Applications of the Rank-Nullity Theorem}

\textbf{Prop 2.4.2/2.4.7:} Let $T: V \rightarrow W$ be a linear map. Then
\begin{enumerate}
    \item $T$ is injective iff ker($T$) = \{$\bar 0_v$\}
    \item $T$ is surjective iff im($T$) = $W$.
\end{enumerate}

% \bigskip 

\noindent
\textbf{Corollary [Rank-Nullity]:} Suppose $T: V \rightarrow W$ is a linear map, where $V$ is finite dimensional. Then
\begin{enumerate}
    \item $T$ is injective iff dim(im($T$)) = dim($V$) 
    \item If dim($W$) $<$ dim($V$) then $T$ is not injective
    \item If dim($W$) $< \infty$ then $T$ is surjective iff dim(im($T$)) = dim($W$)
    \item If dim($V$) $<$ dim($W$) then $T$ is not surjective
    \item If dim($V$) = dim($W$) then $T$ is injective iff $T$ is surjective
    \item If dim(W) $\ne$ dim($V$) then $T$ is not bijective.   
\end{enumerate}

\noindent 
\textbf{Prop:} Let $T: V \rightarrow W$ be a linear map and let $\bar w \in $ im($T$). Take any vector $\bar v \in T^{-1}(\{\bar w\})$. Then $T^{-1}(\{\bar w\}) = \bar v + $ ker($T$)

\bigskip

\noindent 
\textbf{Corollary:} Let $T: V \rightarrow W$ be a linear map between finite dimensional vector spaces and let $\bar w \in W$. Then there is a unique vector $\bar v \in V$ such that $T(\bar v) = \bar w$ iff 
\begin{enumerate}
    \item $\bar w \in $ im($T$)
    \item ker($T$) = \{$\bar 0_v$\} 
\end{enumerate}
In this case, $T^{-1}(\{\bar w\}) = \{\bar v\}$


\section*{Definitions}
\textbf{Def:} Let $S_1, S_2$ be sets. A function $f: S_1 \rightarrow S_2$ is said to be 
\begin{enumerate}
    \item \textit{injective} (or \textit{one-to-one}) if $\forall x,y \in S_1$, if $f(x) = f(y)$ then $x = y$.
    \item \textit{surjective} (or \textit{onto}) if $\forall z \in S_2, \; \exists x \in S_1$ s.t. $f(x) = z$. 
    \item \textit{bijective} if $f$ is both injective and surjective. 
\end{enumerate}

\noindent 
\textbf{Def:} Let $T: V \rightarrow W$ be a linear map and fix any vector $\bar w \in W$. Then the \textit{inverse image} (\textit{preimage}) of $\bar w$ under $T$ is the set $T^{-1}(\{\bar w\}) := \{\bar v \in V \mid T(\bar v) = \bar w\}$ 